Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
moving the memory layout paragraph

In term of memory layout, we adopt a format similar to the ELLPACK
format to store the matrix since the number of nonzeros per row is
constant throughout the matrix. The matrix is given in two arrays. The
first one is the classical {\tt col\_id} array that describes the
sparsity structure of the matrix. Each row of {\tt col\_id} consists of $n_z$
entries that label the column index of each nonzero in $A$. The
other array is the {\tt data} array that gives the values of the 
nonzeros in the four matrices. The values of the matrices are interleaved
so that the value $A^l_{col\_id[k]}$ of the $k$th nonzero of the
$l$th matrix is at index $(k-1)*4+l-1$. The vectors {\tt x} are 
interleaved so that {\tt x}$^l_i$ and {\tt x}$^{l+1}_i$ are
consecutive in memory. The vector {\tt y} is similarly
interleaved. This is schematically shown in Figure~\ref{fig:mat_struct}, 
where the elements of $y$ are grouped in sets of 16, which correspond
to four derivatives applied to four functions, at a single point. \todo{this description is innacurate.}

@@

>>>>

@@

In term of memory layout, we adopt a format similar to the ELLPACK
format to store the matrix since the number of nonzeros per row is
constant throughout the matrix. The matrix is given in two arrays. The
first one is the classical {\tt col\_id} array that describes the
sparsity structure of the matrix. Each row of {\tt col\_id} consists of $n_z$
entries that label the column index of each nonzero in $A$. The
other array is the {\tt data} array that gives the values of the 
nonzeros in the four matrices. The values of the matrices are interleaved
so that the value $A^l_{col\_id[k]}$ of the $k$th nonzero of the
$l$th matrix is at index $(k-1)*4+l-1$.  \todo{this description is innacurate.} The vectors {\tt x} are 
interleaved so that {\tt x}$^l_i$ and {\tt x}$^{l+1}_i$ are
consecutive in memory. The vector {\tt y} is similarly
interleaved, grouped in sets of 16, which correspond
to four derivatives applied to four functions, at a single point.
